---
title: "miniproject_3"
author: "Emma King and Tasaday Green"
date: "11/13/2017"
output: html_document
---
---
title: "MP3_Draft"
author: "Emma King"
date: "November 19, 2017"
output: html_document
---


```{r}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```

```{r}
test <- db %>%
  dbGetQuery("SELECT ml.movie_id, ml.linked_movie_id, ml.link_type_id, 
	   t1.id AS original_id, t2.id AS sequel_id, 
       t1.title AS original, t2.title AS sequel,
       t1.kind_id AS kind_id1, t2.kind_id AS kind_id2,
       t1.production_year AS year1, min(t2.production_year) AS first_sequel,
       min(t2.production_year) - t1.production_year AS time_diff
FROM movie_link AS ml
JOIN title AS t1
ON ml.movie_id = t1.id 
JOIN title AS t2
ON ml.linked_movie_id = t2.id
WHERE ml.link_type_id = 2
AND t1.kind_id = 1
AND t2.kind_id = 1
GROUP BY original_id
ORDER BY time_diff;
")
```

```{r}
test1 <- db %>%
  dbGetQuery("SELECT ml.movie_id, ml.linked_movie_id, ml.link_type_id, 
	   t1.id AS original_id, t2.id AS sequel_id, 
       t1.title AS original, t2.title AS sequel,
       t1.kind_id AS kind_id1, t2.kind_id AS kind_id2,
       t1.production_year AS year1, min(t2.production_year) AS first_sequel
FROM movie_link AS ml
JOIN title AS t1
ON ml.movie_id = t1.id 
JOIN title AS t2
ON ml.linked_movie_id = t2.id
WHERE ml.link_type_id = 2
AND t1.kind_id = 1
AND t2.kind_id = 1
GROUP BY sequel_id;
")
```

```{r}
test2 <- test1 %>%
  group_by(original_id, original, year1) %>%
  summarise(firstsql = min(first_sequel)) %>%
  mutate(time_diff = firstsql - year1)
```

```{r}
test5 <- test %>%
  group_by(year1) %>%
  summarise(avg_td = mean(time_diff))
```

```{r}
test6 <- test2 %>%
  group_by(firstsql) %>%
  summarise(avg_td = mean(time_diff))
```

## Are there more sequels in recent years? (count)

```{r}
test1 %>%
  mutate(tempgap = first_sequel - year1) %>%
  filter(tempgap > 0, first_sequel < 2018) %>%
  group_by(first_sequel) %>%
  summarise(N = n()) %>%
  ggplot(aes(x = first_sequel, y = N)) +
  geom_point()
```


## Are sequels happening faster?

#### Average time difference between original movie and sequel by production year of the sequel

```{r}
ggplot(test6, aes(x = firstsql, y = avg_td)) +
  geom_point()
```

#### Average time difference between original movie and sequel by production year of the original year

```{r}
ggplot(test5, aes(x = year1, y = avg_td)) +
  geom_point()
```


## Are sequels occuring faster

#### Time difference between a novie and it's sequel by year of the original movie's production year

```{r}
ggplot(test2, aes(x = year1, y = time_diff)) +
  geom_point(alpha = 0.2)
```

#### Time difference between a sequel and the original movie by the production year of the sequel

```{r}
ggplot(test2, aes(x = firstsql, y = time_diff)) +
  geom_point(alpha = 0.2)
```


## Remakes

```{r}
db %>%
  dbGetQuery("SELECT *
             FROM link_type")
```

```{r}
test7 <- db %>%
  dbGetQuery("SELECT ml.movie_id, ml.linked_movie_id, ml.link_type_id, 
	   t1.id AS original_id, t2.id AS sequel_id, 
       t1.title AS original, t2.title AS sequel,
       t1.kind_id AS kind_id1, t2.kind_id AS kind_id2,
       t1.production_year AS year1, min(t2.production_year) AS first_sequel
FROM movie_link AS ml
JOIN title AS t1
ON ml.movie_id = t1.id 
JOIN title AS t2
ON ml.linked_movie_id = t2.id
WHERE ml.link_type_id IN (2, 4, 8, 12)
AND t1.kind_id = 1
AND t2.kind_id = 1
GROUP BY sequel_id;
")

test7$link_type_id <- as.character(test7$link_type_id)
```

### In Hollywood

```{r}
test8 <- db %>%
  dbGetQuery("SELECT ml.movie_id, ml.linked_movie_id, ml.link_type_id, 
	   t1.id AS original_id, t2.id AS sequel_id, 
       t1.title AS original, t2.title AS sequel,
       t1.kind_id AS kind_id1, t2.kind_id AS kind_id2,
       t1.production_year AS year1, min(t2.production_year) AS first_sequel,
       cn.id AS cn_id, cn.country_code, mc.company_id, mc.movie_id AS mc_id
FROM movie_link AS ml
JOIN title AS t1
ON ml.movie_id = t1.id 
JOIN title AS t2
ON ml.linked_movie_id = t2.id
JOIN movie_companies AS mc
ON ml.movie_id = mc.movie_id
JOIN company_name AS cn
ON cn.id = mc.company_id
WHERE cn.country_code = '[us]'
AND ml.link_type_id IN (2, 4, 8, 12)
AND t1.kind_id = 1
AND t2.kind_id = 1
GROUP BY sequel_id") 

test8$link_type_id <- as.character(test8$link_type_id)
```

```{r}
test8 %>%
  mutate(tempgap = first_sequel - year1) %>%
  filter(tempgap > 0, first_sequel < 2018) %>%
  group_by(link_type_id, first_sequel) %>%
  summarise(N = n()) %>%
  ggplot(aes(x = first_sequel, y = N, color = link_type_id)) +
  geom_point() +
  geom_smooth()
```

```{r}
test7 %>%
  mutate(tempgap = first_sequel - year1) %>%
  filter(tempgap > 0, first_sequel < 2018) %>%
  group_by(link_type_id, first_sequel) %>%
  summarise(N = n()) %>%
  ggplot(aes(x = first_sequel, y = N, color = link_type_id)) +
  geom_line()
```

